Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2023-12-22 main.tex
:zap: Refactor code

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/pc_power_sx.tex}
			}
			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_power_sx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_power_bond_nd.tex}
				}
			}
			\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_power_bond_hd.tex}
				}
			}
			\caption{Average channel power versus \gls{ris} group size $L$ for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_power_bond}
		\end{figure}
		% Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
		% The behavior is more obvious for a large \gls{ris}.
		This behavior is more pronounced for a large \gls{ris}.
		For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
		% As $L$ increases from 1 to 2,
		It implies that the channel shaping capability of \gls{bd} \gls{ris} scales with group size $L$.

@@

		The complex derivative of \eqref{ob:pc_rate} w.r.t. \gls{ris} block $g$ is
		\begin{equation}
			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\sigma_n^2} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
			\label{eq:pc_rate_gradient_ris}
		\end{equation}
		Algorithm~\ref{ag:pc_rate_ris} summarizes the adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem.

		\setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			\small
			\caption{\gls{rcg} Method for \gls{ris} \gls{mimo}-\gls{pc} Rate Maximization}
			\label{ag:pc_rate_ris}
			\begin{algorithmic}[1]
				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\sigma_n^2$
				\Ensure $\mathbf{\Theta}^\star$
				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
				\Repeat
					\State $r \gets r+1$
					\For {$g \gets 1$ to $G$}
						\State $\mathbf{\Theta}_g^{(r)} \gets$ \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian}--\eqref{eq:rcg_update}
					\EndFor
				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/pc_rate_sx.tex}
			}
			\caption{Average achievable rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_rate_sx}
		\end{figure}

@@

	\begin{subsection}{Channel Singular Value Redistribution}
		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
		\begin{equation}
			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
			\end{bmatrix}.
		\end{equation}
		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
		\begin{figure}
			\centering
			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris} for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ without direct link.}
			\label{sm:pc_singular_toy}
		\end{figure}
		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
		Larger gaps are expected when the symmetry constraint can be relaxed.

@@

		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		where $\rho_n$ is the weight of $n$-th singular value.
		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
		\begin{equation}
			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
			\label{eq:pc_singular_gradient_ris}
		\end{equation}
		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.

		\begin{figure}[!t]
			\centering
			\subfloat[Pareto Front\label{sm:pc_singular_pareto_bond}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_singular_pareto_bond.tex}
				}
			}
			\subfloat[Evolving Trend\label{sm:pc_singular_trend_bond}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_singular_trend_bond.tex}
				}
			}
			\caption{Singular value Pareto front and trend for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 16, 2)$.}
			\label{sm:pc_singular_bond}
		\end{figure}
		The Pareto front and evolving trend of channel singular values are shown in Fig.~\subref*{sm:pc_singular_pareto_bond} and \subref*{sm:pc_singular_trend_bond}.
		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
	\end{subsection}
\end{section}

@@

		\begin{proposition}
			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
			\end{equation}
			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
			\end{equation}
			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - \mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}$ and
			\begin{equation}
				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
			\end{equation}
		\end{proposition}
		\begin{proof}
			To be added.
		\end{proof}

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/ic_interference_sx.tex}
			}
			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$. Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}. Reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB} and $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$.}
			\label{sm:ic_interference_sx}
		\end{figure}
		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
	\end{subsection}

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/ic_rate_sx.tex}
			}
			\caption{Average weighted sum-rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
			\label{sm:ic_rate_sx}
		\end{figure}
		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
	\end{subsection}
\end{section}

>>>>

% optidef
\DeclareDocumentEnvironment{customopti}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
	\ifthenelse{\equal{#3}{b}}{%
		\ifthenelse{\equal{#1}{s}}%
		% Short version problem
		{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
		% Long version problem
		{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
	}{%
		\ifthenelse{\equal{#1}{s}}%
		% Short version problem
		{\setFormatShort{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
		% Long version problem
		{\setFormatLong{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
	}%
}%
{\endBaseMini\toggletrue{bodyCon}}

\DeclareDocumentEnvironment{customopti*}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
	\ifthenelse{\equal{#1}{s}}%
	% Short version problem
	{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
	% Long version problem
	{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
}{\endBaseMiniStar\toggletrue{bodyCon}}

\DeclareDocumentEnvironment{customopti!}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
	\ifthenelse{\equal{#1}{s}}%
	% Short version problem
	{\setFormatShort{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
	% Long version problem
	{\setFormatLong{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
}{\endBaseMiniExclam\toggletrue{bodyCon}}

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/pc_power_sx.tex}
			}
			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$. $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_power_sx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_power_bond_nd.tex}
				}
			}
			\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_power_bond_hd.tex}
				}
			}
			\caption{Average channel power versus \gls{ris} group size $L$. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_power_bond}
		\end{figure}
		% Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
		% The behavior is more obvious for a large \gls{ris}.
		This behavior is more pronounced for a large \gls{ris}.
		For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
		% As $L$ increases from 1 to 2,
		It implies that the channel shaping capability of \gls{bd} \gls{ris} scales with group size $L$.

@@

		The complex derivative of \eqref{ob:pc_rate} w.r.t. \gls{ris} block $g$ is
		\begin{equation}
			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
			\label{eq:pc_rate_gradient_ris}
		\end{equation}
		Algorithm~\ref{ag:pc_rate_ris} summarizes the adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem.

		\setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			\small
			\caption{\gls{rcg} Method for \gls{ris} \gls{mimo}-\gls{pc} Rate Maximization}
			\label{ag:pc_rate_ris}
			\begin{algorithmic}[1]
				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\eta$
				\Ensure $\mathbf{\Theta}^\star$
				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
				\Repeat
					\State $r \gets r+1$
					\For {$g \gets 1$ to $G$}
						\State $\mathbf{\Theta}_g^{(r)} \gets$ \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian}--\eqref{eq:rcg_update}
					\EndFor
				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{sm:pc_rate_sx}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_rate_sx.tex}
				}
			}
			\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{sm:pc_rate_tx}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/pc_rate_tx.tex}
				}
			}
			\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
			\label{sm:pc_rate}
		\end{figure}

@@

	\begin{subsection}{Channel Singular Value Redistribution}
		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
		\begin{equation}
			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
			\end{bmatrix}.
		\end{equation}
		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
		\begin{figure}
			\centering
			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
			\label{sm:pc_singular_toy}
		\end{figure}
		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
		Larger gaps are expected when the symmetry constraint can be relaxed.

@@

		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
		% \begin{maxi!}
		% 	{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		% \end{maxi!}

		\begin{customopti!}
			{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{customopti!}

		where $\rho_n$ is the weight of $n$-th singular value.
		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
		\begin{equation}
			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
			\label{eq:pc_singular_gradient_ris}
		\end{equation}
		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/pc_singular_pareto.tex}
			}
			\caption{Singular value Pareto front. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
			\label{sm:pc_singular_pareto}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/pc_singular_bound.tex}
			}
			\caption{Singular value bounds for rank-1 indirect channel. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
			\label{sm:pc_singular_bound}
		\end{figure}

		The Pareto front and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
	\end{subsection}
\end{section}

@@

		\begin{proposition}
			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
			\end{equation}
			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
			\end{equation}
			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
			\begin{equation}
				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
			\end{equation}
		\end{proposition}
		\begin{proof}
			To be added.
		\end{proof}

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/ic_interference_sx.tex}
			}
			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$. Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}. $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
			\label{sm:ic_interference_sx}
		\end{figure}
		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
	\end{subsection}

@@

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/ic_rate_sx.tex}
			}
			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$. $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
			\label{sm:ic_rate_sx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/ic_rate_user.tex}
			}
			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$. $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
			\label{sm:ic_rate_user}
		\end{figure}

		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
	\end{subsection}
\end{section}
